Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-04 testbed.tex
testbed needs some more work

@@

@@

@@

@@

% Create an initramfs
\begin{lstlisting}[]
# How to i know the kernel version /lib/modules/
# mkinitramfs -o /boot/init.gz -k 4.4.11+
\end{lstlisting}
\FloatBarrier

@@

% Exit chroot, umount, and write to memory card
\begin{lstlisting}[]
# exit
# cd ..
# umount --recursive ${ROOTDIR}
# losetup -d WHICH_NUMBE.img
# dd if=${IMAGE}.img of=/dev/mmcblk0 bs=4M
\end{lstlisting}
\FloatBarrier

How about kodo python?

>>>>

We installed git in a previous step, so lets clone the repository. The below
code stores it in /tmp which is really mounted in \ac{RAM}. Thus, the files
will disappear when the machine is rebooted.

@@

To enable the overlaying filesystem it is required to generate an initial \ac{RAM}
file system (initramfs). Initramfs is an initial filesystem that gets loaded into
\ac{RAM} during the startup process of a linux machine to prepare the real
filesystem.

For this purpose, we need BuxyBox:

@@

Add and activate the overlaying filesystem, we need to add the scripts and tell initramfs
to load the overlaying filesytem:

@@

Raspbian lite uses a "u-boot" to boot, so it should be made aware of the
initramfs that we will generate.

@@

Finally, lets generate the image. This is done using "mkinitramfs", that will
by default look for the kernel modules of the current system. Remember we are
chrooted, so we need to specify the correct kernel modules to look for. These
can be found in "/lib/modules".

% Create an initramfs
\begin{lstlisting}[]
# ls /lib/modules/
\end{lstlisting}
\FloatBarrier

For \ac{Raspi} 1, our kernel modules was "4.4.11+". The other modules in /lib/modules
is for \ac{Raspi} 2.

Thus, to run mkinitramfs, type in the correct kernel version:

% Create an initramfs
\begin{lstlisting}[]
# mkinitramfs -o /boot/init.gz -k 4.4.11+
\end{lstlisting}
\FloatBarrier

This should generate a new initial \ac{RAM} filesystem that will overlay a \ac{RAM} filesystem.

@@

The final step is to write the image to all the memory cards before they can
be plugged in the \ac{Raspi}s. This is done by first leaving the chrooted filesystem
and unmounting all the directories we mounted:

% Exit chroot, umount, and write to memory card
\begin{lstlisting}[]
# exit
# cd ..
# umount --recursive ${ROOTDIR}
# losetup -d WHICH_NUMBE.img
\end{lstlisting}
\FloatBarrier

If successfully unmounted, you can insert a memory card in your machine. In our
system, this memory card was available under /dev/mmcblk0, but this may be
different on different machines. For internal memory card readers, it will
probably be named /dev/mmcblkX where X is some number and if the memory card
reader is connected through \ac{USB}, then it is likely called /dev/sdX.
Make sure to write to the correct device as everything will be overwritten!

Below is a few commands that may help you to deduce which device is correct:

\begin{lstlisting}[]
# lsblk
# df -h
\end{lstlisting}
\FloatBarrier

For us, the device was /dev/mmcblk0, so we write the image to that device:
\begin{lstlisting}[]
# dd if=${IMAGE}.img of=/dev/mmcblk0 bs=4M
\end{lstlisting}
\FloatBarrier

\subsection{Kodo python}
